State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-25 prism-backend/research/soa_review/ac.tex
Some writeup on ACs main approaches, security models, and functionality. Doc reorg.

\todo{Big: Brands's line of works (U-prove).}

\begin{enumerate}
\item Main intuition.
\item Evolution of main security models.
\item Variations concerning functionality.
\item Evolution in efficiency.
\item Main issues.
\item Approx. number of related works in main crypto+security venues: IACR,
  Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs...
\end{enumerate}

Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
further studied, formally treated, and optimized, in a series of papers by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} and, independently, by Brands
\needcite\footnote{Camenisch and Lysyanskaya line of work is well known for
  IBM's Idemix system, and Brands's work for Microsoft's U-Prove. More detail
  appears in the sequel.}. In an AC system, roughly speaking, users receive
credentials from an issuing organization, which they can then use to
authenticate against some verifier. The main property is that this
authentication process can be done in a privacy-preserving way. This typically
means that the verifier cannot link different authentication processes by that
same user. Usually, credentials are composed by multiple attributes, such that
the verifier only learns the attributes that the user is willing to share (or a
function of them).

\subsection{Approaches, Models, and Variations}

\paragraph{Main approaches.} %
The more fruitful line of work within the AC domain is the one initiated by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} (henceforth, CL credentials or,
when referring to the underlying signature schemes defined in \cite{cl02,cl04},
CL signatures). The core idea is simple: in order to build a (basic) AC
system, all that is needed are a commitment scheme, and a signature scheme
with efficient protocols for signing committed values, and proving knowledge
of a signature. From this, a basic AC system can be derived as in \figref{XXX}.
Essentially:

\begin{itemize}
\item User $A$ randomly produces a secret value $s_A$, and commits to it,
  producing $c_A$.
\item User $A$ interacts with issuer $I$ to get a signature on $s_A$. To
  avoid leaking the secret to $I$, $A$ uses $c_A$, proving knowledge of the
  associated secret. The produced signature $\sigma_A$, is $A$'s anonymous
  credential.
\item When $A$ needs to convince a verifier $B$ that she owns a valid credential
  issued by $I$, she just has to create a zero-knowledge proof of knowledge
  of $\sigma_A$.
\end{itemize}

@@

Restricting the expressiveness, and focusing on letting the credential holder
reveal only a subset of the attributes in a credential, more efficient schemes
have been proposed, leveraging algebraic tricks such as structure-preserving
signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
interpolation to allow revealing only a subset of the committed messages;
\todo{what was the specific technique of \cite{fhs19}?}. \cite{fhs19}, is more
efficient, as avoids complex zero-knowledge proofs; however it does not support
blind issuance of credentials, as opposed to \cite{cdhk15} \todo{confirm this
  last part, and refine}.

\todo{Mention the subline of delegatable credentials, with controlled
  malleability.}

All AC systems mentioned up to this point follow, up to small variations, the
same approach: randomizable signatures on sets of (committed) messages, with
(somehow) efficient proofs. \todo{Move to the ones based on predicate
  encryption.}

\todo{End with the MAC-based approach.}

\begin{enumerate}
\item[\cite{cl01}:]
  \begin{itemize}
  \item Functionality: FormNym, GrantCred, VerifyCred, VerifyCredOnNym.
  \item Approach: Users create a pseudonym with each organization. For this,
    they have to register first with the organization (associating a key to
    a user name). Whenever the user wants to get a credential from a organization
    in which he registered, he has to authenticate, and then the organization
    decides whether or not to grant the credential. Users can show their
    credentials to organizations in two ways: (1) just proving that they own a
    credential issued by some organization; or (2), proving that they own a
    credential issued by some organization \emph{and} this credential is over
    the same pseudonym that the user holds with the verifying organization.
    Essentially, pseudonyms are the concatenation of two random numbers (one
    provided by the user, and the other by the organization). They get
    associated an authenticating tag, which is a statistically hiding commitment
    to the user secret (computed using randomness provided by both user and
    organization). Organizations keep a database of the generated pseudonyms.
    To get a credential from an organization where the user registered
    previously, the user proves knowledge of the secret involved in the
    pseudonym. The organization then creates a ``random signature'' (by using a
    the inverse of random exponent, with the help of the factorization of an RSA
    modulus chosen by the organization at setup time) over the pseudonym, and
    gives that to the user. Users can show the credentials (in any of the
    previously stated two ways) by creating non-interactive zero-knowledge
    proofs of knowledge of the appropriate secret. Note that, in case (2),
    this means that the proof is over two pseudonyms, which must share the
    same secret.    
  \end{itemize}
\item[\cite{cl02}:]
  \begin{itemize}
  \item Approach: Te paper aims at improving efficiency of AC systems, as
    well as still ensuring that the user can retrieve their credentials in
    a privacy-preserving manner. For this purpose, the core of the paper
    describes a signature scheme that allows signing blocks of messages,
    and later prove, in zero-knowledge, knowledge of such a signature. To
    enable private retrieval of credentials, the authors describe a protocol
    for their signature scheme, whereby the user specifices a commitment to
    a message (or a block of messages, although this is not actually
    formalized), and get a signature of the message in return. While the
    authors do not strictly define an AC system, the application of their
    signature system and related protocols to the AC domain seems direct.
    Indeed, the same functionality as in \cite{cl01} seems straight
    forward given the cryptosystems in \cite{cl02}.
  \end{itemize}
\item[\cite{cl04}:] Follows a similar approach to \cite{cl02}, although
  changing the security assumptions to be based only on problems related
  to the discrete logarithm, and on bilinear maps. Basically, defines a
  signature scheme suitable for signing multiple messages, a protocol to
  obtain a signature on a committed value, and a protocol to prove knowledge
  of a signature. Concerning commitments, they rely on Pedersen commitment
  scheme, for which protocols are known to prove knowledge and equality of
  committed values. This lets them follow the same approach to \cite{cl02},
  which is in turn the one in \cite{cl01}.
\item[\cite{bcc+09}:] This is mostly a theoretical work, which is relevant
  since it is (one of) the first to propose a delegatable anonymous
  credentials systems. The building blocks are randomizable proofs of
  knowledge that randomize both the proof and the statement (which the authors
  build on top of Groth-Sahai proofs), and message authenticators (a variant
  of signatures that require a special notion of unforgeability). Each user
  can create pseudonyms, which are commitments to his secret key, and use
  these commitments to prove ownership of and delegate credentials. These
  pseudonyms are essentially as in the CL line of work (user with pseudonym
  $N^A_U$ w.r.t. organization $A$ and $^B_U$ w.r.t. orgainzation $B$, can
  prove to $B$ (resp. $A$) that $N^A_U$ and $N^B_U$ are related to the
  same secret key). Delegations here follow a sequential order: i.e., if
  a credential has level $L$, then its owner can further delegate this
  credential, and the result would be a credential with level $L+1$. To
  delegate, essentially, the delegator (with pseudonym $N_I$) and delegatee
  (with pseudonym $N_D$) perform an interactive protocol
  through which the delegatee receives a randomizable NIZKP that lets him
  prove knowledge of an authenticator over $N_D$, issued by $N_I$. Since
  both the proof and the statement can be randomized, verifiers do not
  learn the chain of delegation.  Although this is informally mentioned,
  ``attributes'' can be added to the delegation process too (besides to the
  credentials themselves). This is suggested by adding the attributes -- which
  would be visible to the verifier -- to the application of a hash function
  used to derive the authenticator). 
\item[\cite{cks10}:] The system proposed here follows the conventional
  approach to anonymous credentials based on randomizable signatures (with
  the possibility to sign committed values) over vectors of messages.
  It however enables issuers to produce updates on already signed messages.
  This updates can be leveraged to incorporate revocation. Essentially,
  time is divided in epochs, and credentials include an attribute which
  represents the expiration date/epoch of the credential. Users have to
  prove that their credential is valid for the current epoch. Similarly,
  to add new attributes, the issuer leverages the internal structure of
  the signatures over vectors of messages, to basically add new messages
  (attributes). In both cases, it is responsibility of the user to update
  her credential given the latest update by the issuer. An example
  instantiation is given using BBS signatures.
\item[\cite{cmz14}:] This work differs from the rest in that they use
  secret key cryptography rather than public key. Namely, they assume a
  setting in which the issuer will also be the verifier (e.g., a
  transportation organization that issues tickets for its travelers). In
  this setting, it is reasonable to assume that both issuer and verifier
  will have access to the same secret. Therefore, they replace signatures
  with (algebraic) MACs. They do not create pseudonyms for end users (like
  \cite{sms+19}). Other than that, the supported functionality is similar
  to the rest: Setup and KeyGen to initialize the cryptographic parameters,
  and produce the issuer's keys, respectively; an interactive protocol for
  end users to blindly receive credentials (MACs) on their attributes; and
  an interactive protocol for showing and verifying a credential. In case
  that issuance does not need to be blinded, it becomes a non-interactive
  protocol (i.e., the issuer just produces the credential and sends it to
  the user). Otherwise, the user has to encrypt the attributes and prove
  they are correct. Presentation only requires one message from the user
  to the verifier.
\item[\cite{cl11}:] The approach differs from the conventional ones. In this
  case, the focus is on settings where users may want to combine multiple
  credentials from different issuers. Thus, interest is on reducing the size
  of the resulting credentials, and the efficiency of associated processes.
  The approach is based on aggregate signatures. As usual, each credential
  may contain several attributes. Each attribute is independently signed
  by the issuer. Then, users can combine an arbitrary number of signed
  attributes (by the same or different issuers) into a single aggregate
  signature. Verification only needs the aggregated signature and the set
  of public keys of all the involved issuers. To prevent different users
  from aggregating their credentials, the authors resort to \emph{indexed}
  aggregate signatures: an index is added to each signature, such that only
  signatures that have the same index can be aggregated. In their instantiation,
  the signature is a BGLS signature \cite{bgls03}, and the index is a BB
  signature \cite{bb04}. The actual instantiation seems impractical (too many
  linear costs, see the table in the paper).
\item[\cite{cklm14}:] This work is, in essence, a generalization of \cite{bcc+09}.
  The main novel building block are controlled-malleability NIZKs. Basically,
  these are NIZKs that can be re-randomized, but only for a pre-defined set of
  (NP) transformations. From this cm-NIZKs, malleable signatures are built.
  From malleable signatures and commitments, delegatable credentials are built
  as follows. Credentials are basically a tuple $(nym, l, flag)$, where $nym$
  is a commitment to the user's private key, $l$ is the length of the credential
  in the delegation chain, and $flag$ is either $cred$ or $proof$. Credentials
  are accompanied with a malleable signature (which, for level 1 credentials,
  it is a signature by the issuer). To create ``proofs'' or to delegate, the
  credential owner has to apply one of the two allowed transformations. For
  ``proofs'', basically the transformation that has to be applied to the original
  proof (malleable signature) converts it to a proof showing that the prover
  knows the secret in the ``source'' pseudonym and ``target'' pseudonym, and
  both are the same. In the case of delegations, flag is set to ``cred'', and
  the transformation converts the cm-NIZK proof into one that lets the prover
  prove knowledge of the secret key in the ``source'' pseudonym, and allows
  only to produce a new credential with structure $(nym', l+1, cred)$ -- i.e.,
  from a credential of level $l$, only a credential of level $l+1$ can be
  derived. On the delegation topic, the type of delegation this work ``supports'',
  at least by default, is the simple one of hierarchical delegation.
\item[\cite{cdhk15}:] The approach to build anonymous credentials is roughly
  the same as in the previous works \cite{cl01,cl02,cl04}, although with
  relevant differences that make it more efficient. Basically, users create
  pseudonyms derived from a common secret. Then, any user can request a
  credential. For this, the user needs to prove knowledge of the pseudonym's
  secret. In return, the issuer produces an ``unlinkable redactable signature''
  on a set of attributes, for that pseudonym. A redactable signature is
  essentially a signature over a set (block) of messages, that enables
  subsequent verification that a subset of those messages was signed. This
  is essentially the same as in \cite{cl02,cl04}. However, to achieve
  unlinkability, \cite{cdhk15} incorporates efficient zero-knowledge proofs
  to prove correctness of the subset of the messages that a user wants to
  ``show'' in a credential showing process. This ensures unlinkability (hence,
  privacy). The internal scheme used for this is a vector commitment scheme
  that uses Lagrange interpolation to allow checking that a subset of the
  committed messages are indeed contained within the commitment. Moreover,
  both the vector commitment scheme, and the vector signing scheme, are
  structure preserving. This means that, since all the produced messages,
  commitments, and signatures, are elements of the group (rather than of the
  field), proving knowledge is much more efficient (e.g., it prevents costly
  extraction required for security proofs).
\item[\cite{ckl+15}:] Follows the conventional approach: a secure commitment
  scheme with proofs of knowledge, and a signature scheme that allows to
  sign vectors of messages, including commitments. Here, as in the seminal
  works by Camenisch and Lysyanskaya \cite{cl01,cl02,cl04}, pseudonyms are
  used as explicit building blocks. \todo{Not sure yet of how they are
    made explicit in the generic construction. Clarify.}
  A ``syntactic'' variation: they introduce
  the concept of tokens both for credential issuance and presentation. To
  request issuance of a credential, users have to produce an issuance token
  from the set of attributes they want to reveal to the issuer, and the set
  of attributes they want to hide (potentially coming from another credential
  already owned by the user). An equivalent description applies for presentation
  of a credential to a verifier. In both cases, the issuer/verifier has to
  check the received token prior to issuing a credential or granting access.
  They also add revocation functionality. For this, a revocation authority
  (not necessarily the issuer) keeps a revocation information list, which is
  basically a list containing no longer valid attributes. In order to prove
  that their credentials are valid w.r.t. some attribute, users have to generate
  a (non) revocation token, which proves that the attribute has not been
  included in the revocation information list.
\item[\cite{dmm+18}:] Follows a completely different approach to (most) other
  works. Instead of using randomizable signatures (over committed values) or
  some equivalent building block, it relies on predicate encryption.
  Essentially, a user with attributes $A$ is given a decryption key for a
  predicate $f_A(g)$ which, given a predicate $g$, returns $g(A)$. When
  a verifier wants to check if a user has a set of attributes that meet
  certain policy $h$, challenges the user to decrypt a ciphertext over
  a random message that has been associated to predicate $h$. Then, only
  if the attribute set $A$ of the user meets policy $h$, the user will be
  able to decrypt the random message (since $f_A(h) = h(A) = 1$). This
  protocol is actually augmented with some commitments, to prevent
  misbehaviour from user and from verifier, but the approach is the same.
  \doubt{There is something weird here, or that I do not understand --
    predicate encryption requires a
    set of attributes for encryption, rather than another predicate. I have
    reached out to the authors to see if they can help me clarify this.}
\item[\cite{fhs19}:] Based on Structure Preserving Signatures from equivalence
  classes (SPS-EQ). The approach resembles that of \cite{ckl+15} in that it
  uses a structure preserving primitive, and signs (commitments of) sets of
  messages. However, they aim to avoid (as they claim) costly zero-knowledge
  proofs. Basically, upon setup, a set commitment scheme is set up. Each user
  generates a keypair. To obtain a credential on a set of attributes $A$, the
  user proves knowledge of the user secret key, which is used as randomness
  for a set commitment over $A$. The issuer (proves knowledge of the secret
  key and) returns a SPS-EQ signature over $A$. To show the credential, the
  user randomizes the commitment set and the signature, reveals the required
  subset $D$ of $A$, and computes a witness that indeed $D \subset A$, as well
  as a proof knowledge of the randomness used to randomize the credential (to
  prevent replays). 
\item[\cite{sms+19}:] The Coconut system follows a similar approach than the previous
  works with respect to the representation and showing protocol for credentials.
  Namely, credentials are randomizable signatures issued blindly. In this case,
  the authors rely on Pointcheval Sanders signatures \cite{ps16} as main
  building block, to which they incorporate techniques from other schemes to
  support threshold issuance.
\item[\cite{halp20}:] Builds on Coconut credentials and a blockchain -- in theory,
  any blockchain with smart-contract capability, although it seems they are building
  their own blockchain. This paper is in the frontier of academic and industry
  work. On the cryptographic side, the credentials they build are essentially an
  extension of Coconut credentials (although the extension is not described, nor
  formalized). Users can combine multiple Coconut credentials into one Nym
  Credential. In order to control Sybil attacks, Nym Credentials are obtained
  in exchange of Nym Tokens (how users get hold of these, is not described).
  Service Providers receive Nym Tokens in exchange of offering their services
  through the network.
\item[\cite{hs21}:] This work merges AC approaches based on SPS-EQ and aggregate
  signatures, and also introduces the separation between a trusted but restricted
  device, and a less trusted but powerful device typical in DAA systems. The
  former is referred to as \emph{core}, and the latter as \emph{helper}, hence
  the Core-Helper AC (CHAC) acronym. In addition to the previous basic building
  blocks, the system uses a Signature with Flexible Public Keys (SFPK) scheme.
  Roughly, these are signature schemes where the public keys can be randomized,
  but in a manner that no adversary can decide whether two public keys are
  related or not (i.e., if one is a randomization of the other). Users identities
  are SFPK keypairs, where the public part gets signed by the issuer, using an
  AAEQ scheme (Aggregatable Attribute-based Signature Scheme on Equivalence Classes).
  Roughly, an AAEQ scheme is a combination of attribute-based signatures on
  equivalence classes (which the authors combine with Tag-based Signatures on
  Equivalence Classes), and aggregate signatures. In the proposed AAEQ scheme,
  a tag is derived from an attribute an a nonce, which is then ``signed'' (note:
  this tag resembles much the concept of nyms based on scopes). Since signatures
  (and tags) are group elements sharing the same discrete log (the signer's key),
  they can be aggregated easily via multiplication. Hence, for each attribute that
  the issuer wants to grant to the user, it creates an independent signature where
  the tag depends on the attribute to grant. Then, the user can just aggregate
  all of them into one credential. In addition to this, the authors split the
  operations (which are in the bilinear setting), in a way that requires the
  core to perform only a few operations in $G_1$. The result seems to be quite
  efficient. However, it only supports selective disclosure (no advanced
  privacy-preserving policies), and even revocation is not considered from scratch,
  although the authors sketch an approach to integrate it -- which probably
  would require a more formal analysis and would incur in (possibly bad?)
  added costs.
  \note{The concept of aggregation here is different than the one in \cite{cl11}.
    In the latter, users can aggregate credentials from different issuers. Here,
    this is not possible, as aggregation won't work for different signing keys
    (i.e., issuer keys). Hence, aggregation rather refers to receiving multiple,
    independently signed, attributes by the same issuer, and then combining them
    into a single credential by that same issuer.}
\end{enumerate}

\paragraph{Main security models.}

\begin{enumerate}
\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
  using the ideal-world/real-world paradigm. The authors describe a
  simulator for the operations supported by the system (Setup, FormNym,
  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
  simulator is indistinguishable from that of the real protocol, under the
  strong RSA and Diffie-Hellman assumptions.  
\item[\cite{cl02}:] No security model is given for the anonymous credential
  application of the signature scheme (reasonably, as it is not the main focus
  of the paper). The signature scheme is proven secure (no specific mention
  to a security model, although I suppose it would be quite straight forward)
  based on the Strong RSA and Diffie-Hellman assumptions.
\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
  AC system). The custom proofs are based on the DDH and LRSW assumptions.
\item[\cite{bcc+09}:] The article follows a game-based definition approach,
  with two security properties (besides correctness): anonymity and
  unforgeability, which are the usual, but extended to the scenario with
  delegation. Basically, the anonymity (in the ideal/real world paradigm)
  property requires that the adversary should not distinguish real credentials
  from simulated ones. Moreover, the adversary should not learn the delegation
  chain of an honest credential (even if it was issued by himself). For
  unforgeability, the requirement is that the adversary should not create
  a delegation chain that includes a delegation by an honest user, if the
  user did not actually perform that delegation.
\item[\cite{cks10}:] Signer privacy and user privacy properties are required
  for the underlying signature scheme (thus, inherited by the credential system,
  although I have not found explicit model). Signer privacy captures that the
  adversary (including corrupt users) doesn't learn any information about the
  signer from signatures and updates of signatures. User privacy captures that
  the adversary (including a corrupt issuer) does not learn any information
  about the blindly signed messages. \doubt{Not sure I get the utility of
    signer privacy. The original property seems to come from \cite{bckl08}.}
\item[\cite{cl11}:] The security properties in this work are unforgeability
  and anonymity, for which the authors give game-based definitions.
\item[\cite{cklm14}:] Defines security of the DAC scheme using simulation-based
  notions of anonymity and unforgeability.
\item[\cite{cmz14}:] The security properties proven in this work are:
  \begin{itemize}
  \item \emph{Unforgeability}: The adversary cannot produce a valid proof for a
    statement, if none of the attribute sets for which it has received a
    credential meets that statement.
  \item \emph{Anonymity}: The proofs produced in a presentation do not leak
    more information than the statement being proved.
  \item \emph{Blind issuance}: The issuance protocol is a secure two-party
    protocol for generating credentials on the user's attributes.
  \item \emph{Key-parameter consistency}: no issuer can use different parameters
    to produce credentials of different users such that their anonymity can
    be compromised afterwards. \doubt{This somehow remembers non-frameability in
      group signatures.}
  \end{itemize}
\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
  is very comprehensive, and detailed. Specifically, for the main building block
  (Unlinkable Redactable Signatures), the authors give both game-based
  definitions as well as an ideal functionality. This ideal functionality models
  security in a single-issuer setting. However, as it is done in the UC
  framework, it can be composed with itself, so that a scenario with multiple
  issuers, in which users can combine credentials obtained by different users
  into a single showing process (``presentation'') is directly achievable by
  composing multiple instances of the ideal functionality (one per ``proof
  part'').
\item[\cite{ckl+15}:] The main security and privacy properties required are
  pseudonym collision-resistance (two different user secret keys cannot produce
  the same nym for the same scope), unforgeability (the adversary cannot forge
  issuance tokens or presentation tokens), and privacy (no two presentations by
  the same user can be linked) or weak privacy (presentations by the same user
  can be linked, but not traced to an issuance session). Privacy is modelled
  in the simulation paradigm, the difference in the modelling between privacy
  and weak privacy being a filter that removes some information \note{(I find
    this kind of weird; probably I'm wrong. Would be nice to study further)}.
  The unforgeability and privacy properties are essentially inherited from the
  main building block, privacy-enhancing attribute-based signatures. Although
  there, the authors begin by defining a blind issuance experiment (ensuring
  that the issuer does not learn anything more than what it should during
  isusance), and then define two variants for user privacy: presentation privacy
  and untraceability, which basically match the strong and weak notions for
  PABCs (in untraceability, two presentations by the same user can be linked,
  but not trace to a specific credential issuance). [Strong] user privacy has
  to satisfy both blind issuance and presentation privacy; weak user privacy
  has to satisfy both blind issuance and untraceability. I find this model
  somehow interesting, as it is one of the few (maybe along with \cite{cmz14})
  that includes some notion related to tracing back to issuance of credentials,
  as in group signatures). In both cases (PABC and PABS), [strong] privacy
  implies weak privacy.
  Essentially, the security properties required by the PABC scheme, are
  ensured by the building blocks. Namely: the pseudonym system (requiring
  key extractability, collision resistance and pseudonym unlinkability); the
  revocation scheme (requiring soundness and revocation privacy); the
  PABs (requiring unforgeability, and [weak] privacy); and the commitment
  scheme (requiring blinding and hiding, and opening extractability).
\item[\cite{dmm+18}:] The authors give a game-based security model, covering
  properties of unforgeability, anonymity, and policy-hiding. The latter
  means that, for delegated verification, the verifier is oblivious to the
  policy being verified.
\item[\cite{fhs19}:] Gives a game-based security model, with anonymity and
  unforgeability being the main security properties (besides correctness).
  Unforgeability resembles the traceability property of group signatures,
  which are recognised as an influence in their modelling -- more specifically,
  \cite{bmw03} (the model -- and the oracles therein -- definitely resembles
  the BMW model for GSs). The authors claim to be the firsts to give a well defined and
  formal model for ACs, besides \cite{ckl+15} (which gives game-based properties
  in the simulation paradigm) and \cite{cdhk15} (which follows the UC framework).
  However, \cite{fhs19} claims that adopting non-simulation based definitions
  allows them to reach a more efficient construction. They also support malicious
  issuer key generation, as issuers have to prove knowledge of their secret keys
  (which allows extraction in the games).
  An interesting aspect of their model is that all attributes in their
  credentials are learned by the issuer -- i.e., there are no blindly signed
  attributes. This implies that it is not possible to sign secret keys owned
  by the users (as in the conventional CL credentials). Then, for showing a
  credential, all the user has to do is reveal the attributes s/he is required
  to show. This has the disadvantage that, depending on the use case, this may
  be trivial to attack. For instance, assume a COVID-like pandemic situation,
  in which citizens have to prove being vaccinated. An AC system for this use
  could be naively defined as: { Type of vaccine, Date of vaccination }. But
  this is very susceptible to dictionary attacks, and leaves much to the
  engineering/implementation level. E.g., if it is easy for an eavesdroper
  to get hold of a credential (not even the plaintext attributes), s/he can
  just iterate through the small list of possible values, and then take
  advantage of the ``stolen'' credential. This is certainly secure under the
  model defined in \cite{fhs19}, but it is definitely easy for implementations
  following this model to go wrong...
  They also model only interactive show processes. Furthermore, to prevent
  replay attacks, the user has to prove knowledge of some randomness included
  in the credential. However (\textbf{cross-check this!}), since signatures
  are randomizable without knowledge of any secret value, any adversary that
  learns a credential (not necessarily any plaintext attribute associated to
  it), would be capable of authenticating through a dictionary attack in case
  of small attribute ranges.
  Note: this may just be a modelling issue (or not even that, cross-check later
  in case I misunderstood something). In their construction, they include
  a secret key of the user in the credentials, of which the user has to prove
  knowledge during the issue protocol. They do this by ``reusing'' the user
  secret key as the randomness employed for the set commitment scheme, and
  requiring the user to prove knowledge of the corresponding public key.
  However, I am not sure of whether or not this somehow thwarts the previously
  mentioned ``attack'', which affects the show protocol (\todo{i.e., the user does
    not need to prove knowledge of the usk during show, no?} \note{Actually, it
    should not, as it would probably prevent anonymity}) In any case, even if
  the specific construction and instantiation thwarts this attack, I think their
  model allows it.
\item[\cite{sms+19}:] No security model is given nor adopted.
\item[\cite{halp20}:] No formal definition is given. The following properties
  are claimed: undetectability (this seems similar to traceability in group sigs),
  unlinkability, selective attributes disclosure, unforgeability, persistent
  accounts, sybil resistance, extensibility, availability, decentralization.
\item[\cite{hs21}:] Security is given through game-based definitions of
  unforgeability, anonymity, and dependability. The first two are the usual ones,
  while the latter roughly requires that an adversarial helper cannot produce
  successful showings without cooperation from the core. It would be interesting
  to make a detailed comparison with security models of DAA (usually in the UC
  framework, although some game-based (seemingly flawed) definitions exist).
  The main argument that the authors give when comparing to DAA, is that the

>>>>

\paragraph{Main intuition.}
%
Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
further studied, formally treated, and optimized, in a series of papers by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} and, independently, by Brands
\needcite\footnote{Camenisch and Lysyanskaya line of work is well known for
  IBM's Idemix system, and Brands's work for Microsoft's U-Prove. More detail
  appears in the sequel.}. In an AC system, roughly speaking, users receive
credentials from an issuing organization, which they can then use to
authenticate against some verifier. The main property is that this
authentication process can be done in a privacy-preserving way. This typically
means that the verifier cannot link different authentication processes by that
same user. Usually, credentials are composed by multiple attributes, such that
the verifier only learns the attributes that the user is willing to share (or a
function of them).

\subsection{Approaches, Models, and Variations}
\label{ssec:acapproach}

\subsubsection{Main approaches.}
%
The more fruitful line of work within the AC domain is the one initiated by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} (henceforth, CL credentials or,
when referring to the underlying signature schemes defined in \cite{cl02,cl04},
CL signatures). The core idea is simple: in order to build a (basic) AC
system, all that is needed are a commitment scheme, and a signature scheme
with efficient protocols for signing committed values, and proving knowledge
of a signature. From this, a basic AC system can be derived essentially as
follows:

\begin{enumerate}
\item User $A$, with secret value $s_A$, commits to it into $c_A$.
\item User $A$ interacts with issuer $I$ to get a signature on $s_A$. To
  avoid leaking the secret to $I$, $A$ uses $c_A$, proving knowledge of the
  associated secret. The produced signature $\sigma_A$, is $A$'s anonymous
  credential.
\item When $A$ needs to convince a verifier $B$ that she owns a valid credential
  issued by $I$, she just has to create a zero-knowledge proof of knowledge
  of $\sigma_A$.
\end{enumerate}

@@

Restricting the expressiveness, and focusing on letting the credential holder
reveal only a subset of the attributes in a credential, more efficient schemes
have been proposed, leveraging algebraic tricks such as structure-preserving
signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
interpolation to allow revealing only a subset of the committed messages;
\todo{what was the specific technique of \cite{fhs19}?}. \cite{fhs19}, is more
efficient, as avoids complex zero-knowledge proofs; however it does not support
blind issuance of credentials, as opposed to \cite{cdhk15} \todo{confirm this
  last part, and refine}.
%
Also improving efficiency, but restricting to the scenario in which the issuer
is the same entity as the verifier (as in ticketing systems for public transport),
\cite{cmz14}, replaces signatures with algebraic MACs.

Somewhat similar is the approach to (delegatable) credentials that builds on
signatures with controlled malleability \cite{bcc+09,cklm14}, where \cite{cklm14}
is a generalization of \cite{bcc+09}. Roughly, credentials are signatures, built
from non-interactive zero-knowledge proofs of knowledge, on commitments to the
user key, that support \emph{controlled malleability}. This malleability means
that both the proof and the statements can be randomized and transformed, but
only for allowed transformatoins. The specific transformation considered for
delegation requires that a credential with depth $L$, can only produce a credential
with level $L+1$. Credential showings are also represented through transformations,
through which the holder proves knowledge, and equality, of the secret in the
``source'' and ``target'' nyms. Although the credentials in these works do not
include multiple attributes (some hint on how to support public attributes is
given in \cite{bcc+09}), it is certainly possible to do so through a proper
transformation -- although, probably, the result won't be very efficient if
done naively \todo{specific figures?} The notion of transformations is interesting,
though, as the authors prove that it is similar (or even more generic) than those
used to achieve expresiveness in related digital singature schemes (such as
policy-based signatures \needcite and delegatable functional signatures \needcite).
Thus, it is reasonable to expect that very expressive AC systems could be built
with this approach.

All AC systems mentioned up to this point follow, up to small variations, the
same approach: randomizable signatures on sets of (committed) messages, with
(somehow) efficient proofs. A completely different approach is described in
\cite{dmm+18}, based on predicate encryption. In predicate encryption, given
a master key pair, decryption keys associated with specific predicates can be
derived. Messages, and attribute sets, are encrypted with the master public key,
such that the resulting ciphertext can only be decrypted with a decryption key
associated with a predicate that is satisfied by the attributes in the
ciphertext. Assume an attribute space that can be represented by binary strings
$\Sigma$. On one hand, policies defined by verifiers in \cite{dmm+18} are encoded
as binary circuits through strings in $\Sigma$ too\footnote{\todo{This seems
    like an abuse of predicate encryption, as encryption receives a predicate,
    rather than an attribute set.}}, which can thus be associated to
ciphertexts through the predicate encryption process. On the other hand,
credentials received by users are decryption keys on a generic policy $f$, with
a hardcoded set of attributes (the attributes that the user is granted), that
can evaluate circuits. Then, intuitively, in order for a verifier to check
whether a user owns a attribute-based credential meeting certain policy $g$, it
creates a ciphertext with encoding a circuit for $g$. If the user can decrypt
this ciphertext, the verifier accepts. This only supports public attributes
(i.e., known to the issuer), though. A negative part of this approach is that
credential showings can only be interactive, whereas in the randomizable proofs
approach, they can be made non-interactive too.

\subsubsection{Main Security Models.}
%
All AC systems include \emph{anonymity} and \emph{unforgeability} as main
security properties. Up to minor variations depending on extra functionality,
anonymity typically captures that, concerning a user's credential, nothing
should be learnt by third parties that the user does not explicitly reveal.
E.g., for ACs that support multiple attributes and selectively disclosing
subsets of them, anonymity captures that the information leaked during a showing
of such credential is limited to the subset of attributes voluntarily revealed
by the user. Since multi-show credentials are also the most common type,
anonymity also captures that two different showings must be unlinkable.
As mentioned, further variations in the functionality affect anonymity --
e.g., in systems supporting delegation, the delegation chain may be required
to be kept private.
% 
Concerning unforgeability, it basically captures that no adversary can make
a verifier accept a credential that has not been honestly produced by an
issuer of the system. Again, there are variations to this. For instance, when
credentials are composed of attributes that can further be selectively
disclosed. In this case, the adversary should not be able to prove ownership
of a set of attributes not contained within the set of attributes that have
been leaked.a showing that include attributes not contained in credentials leaked to the
adversary.

Special mention is worth to the model variation in \cite{hs20}, which divides
the user into two entities: core and helper, thus taking anonymous credentials
closer to DAA. This is reflected into the model by adding a property named
\emph{dependability}, which requires that no adversary should be capable to
show an honestly generated credential withouth compromising the core entity.

On the approach to formalize AC security notions, game-based definitions tend
to be more frequent \needcite, also including definitions in the simulation
paradigm. The UC framework has also been used \needcite, even in combination
with game-based definitions \needcite.

\subsubsection{Variations in functionality.}
%
Multi-attribute and multi-show credentials, with selective disclosure, are
the most frequent \needcite.  Blind issuance, i.e., letting users include in
their credentials attributes that are kept hidden from issuers, is also frequent
(and certainly useful to, e.g., include secret keys) \needcite. Delegation has
gained attention in the last decade \needcite, as well as supporting more
expressive proofs. While the latter is indeed possible in the early works
(one can use general zero-knowledge proofs on discrete logarithms given a
CL-, BBS- or PS16- based credential) it is worth noting that the costs are
probably too high, and it also needs to be considered in the model.
%
Perhaps surprisingly, revocation is not a common functionality, although it is
certainly considered by several works \needcite.
%
Threshold issuance is also interesting for decentralized scenarios, but it
was only considered in \cite{sms+19} and, consequently, in \cite{halp20}
(which builds on \cite{sms+19}).
%
And, finally, an interesting variation that only one work seems to target,
is that of efficient aggregation of credentials created by different issuers
\cite{cl11}. As in the topic of expressiveness, this is easily doable with the
conventional approaches: e.g., if the owner of credential A and credential B
wants to use both credentials in the same showing, she just has to prove that
they share the same secret key (although this is only possible in schemes that
embed a user secret within the credential). Still, even if possible and even
supported, this process is inefficient. \cite{cl11} leverages aggregatable
signatures, which target precisely that setting.

\subsubsection{Efficiency.}
%

\subsubsection{Main challenges.}
%

\subsection{Related Primitives}
\label{ssec:acrelated}

\begin{itemize}
\item Anonymous Authentication systems in the line of Nymble, BLACR, PEREA...
\end{itemize}

\subsection{Real World Deployments}
\label{ssec:acrealworld}

\subsection{TODOs}
